Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2022-09-26 tex/sections/apm.tex
Fix readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Producing the required outputs from these inputs is not computationally feasible so the APM receives an auxiliary
input vector $(H,\pi_H,P,\pi_P,R,\pi_R,h)$, where $\pi_X$ is a proof that proves $X$ can be opened w.r.t
$\mathbf{C}_X$ and $h$ is a hint that helps the APM make nondeterministic choices correctly.

@@

The configuration of the APM can be considered as a tuple
\[
(\mathcal{S},\mathcal{L}_{\text{NEU}},\mathcal{L}_{\text{FRU}},\mathcal{T}_{\text{NEU}},
\mathcal{T}_{\text{FRU}})\ ,
\]
where $\mathcal{S}$ is the size of the internal stack, $\mathcal{L}_{\text{NEU}},\mathcal{L}_{\text{FRU}}$ are the
amount of local memory of the normal execution and failure repeater units respectively, and
$\mathcal{T}_{\text{NEU}},\mathcal{T}_{\text{FRU}}$ are the number of cycles that the NEU and FRU runs for. It should
be noted that the APM does not use a different local memory for each application call.

>>>>

Producing the required outputs from these inputs is not computationally feasible, so the APM receives an auxiliary
input vector $(H,\pi_H,P,\pi_P,R,\pi_R,h)$, where $\pi_X$ is a proof that proves $X$ can be opened w.r.t
$\mathbf{C}_X$ and $h$ is a hint that helps the APM make nondeterministic choices correctly.

@@

The configuration of the APM can be considered as a tuple:
\[
(\mathcal{S},\mathcal{L}_{\text{NEU}},\mathcal{L}_{\text{FRU}},\mathcal{T}_{\text{NEU}},
\mathcal{T}_{\text{FRU}})\ ,
\]
where $\mathcal{S}$ is the size of the internal stack, $\mathcal{L}_{\text{NEU}},\mathcal{L}_{\text{FRU}}$ are the
amount of local memory of the normal execution and failure repeater units respectively, and
$\mathcal{T}_{\text{NEU}},\mathcal{T}_{\text{FRU}}$ are the number of cycles that the NEU and FRU runs for. It should
be noted that the APM does not use a different local memory for each application call.

### 2022-09-26 tex/sections/blocks.tex
Update the normal consensus
We removed status blocks and an analysis is added for the effect of online/offline status in the protocol.

Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Fix readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

\begin{center}
    \begin{tabular}{||c||}
        \hline
        \textbf{Block} \\ [0.6ex]
        \hline\hline
        height: $h$                          \\ [1.2ex]
        commitment to the program database: $\mathbf{C}_{P}$             \\ [1.2ex]
        commitment to the heap database: $\mathbf{C}_{H}$               \\ [1.2ex]
        commitment to the ordered list of requests: $\mathbf{C}_{R}$        \\ [1.2ex]
        clustering directives: $dir$                        \\ [1.2ex]
        certificate of the validators assembly for \\
        the block with height $h - k$: $v \mhyphen cert_{h-k}$         \\ [1.2ex]
        certificate of the delegates for\\
        the previous block: $d \mhyphen cert_{h-1}$        \\ [1.2ex]
        previous block hash                           \\ [1.2ex]
        \hline
    \end{tabular}
\end{center}

@@

To validate a block three main conditions need to be validated: (i) commitments to the program and heap
database result from applying the request list and clustering directives of the block to the previous AscEE
state, (ii) $v \mhyphen cert_{h-k}$ is valid, (iii) previous block is valid and has height $h - 1$.

@@

Verifying statement~\ref{eq:ci} can be done by either replaying the AscEE computation and performing the required
preprocessing and postprocessing steps, or alternatively by
verifying a computation proof. To use computation proofs the verifier and prover need to share an arithmetized
representation of $\tau$ and use it for both proof generation and verification.

The Argennon Prover Machine provides a convenient and universal arithmetization for any Argennon
application. Moreover, since a compiled version of every Argennon application to the APM code is stored in the AscEE
program area, validators do not need to locally store the APM code of applications.

The Argennon protocol does not enforce the usage of the APM. Validators and PVC servers can use different methods
for arithmetization. This naturally would require that the ASAR of an application is used
for generating the appropriate arithmetization.

The certificate of validators, $v \mhyphen cert_{h-k}$, is an aggregate signature. Validating it requires accessing the
AscEE heap state at block $h-k-m$ to obtain public keys and stake values. Here $m$ is the total number of validator
assemblies and $k$ is the maximum allowed length of
the unvalidated chain. (See Section\ref{subsec:validators-committee})
Again, in addition to direct verification, a validator can use computation proofs, received from the Argennon cloud,
to perform cheaper verification of this certificate.

For validating the previous block, instead of directly validating the content of the block, a validator only
verifies the block certificates. Verifying $d \mhyphen cert_{h-1}$ is straightforward. Verifying $v \mhyphen
cert_{h-1}$, which should be performed based on stakes at block $h-m-1$, can be cheaply done by using computation
proofs, obtained from
the
Argennon cloud.

@@

In summary, a validator validates a block by verifying three computation proofs: $\pi_{\tau}$ which proves the
transition is correct, $\pi_{h-k}$ which proves the validity of the included certificate of block $h-k$ and $\pi_{h-1}$
which proves the previous block has a correct certificate of validators. It should be noted that these proofs are not
a part of the block contents.

@@

Argennon uses a parallel algorithm to produce block certificates and therefore the signature scheme needs to satisfy
certain properties:
\begin{itemize}
    \item \textbf{Associative aggregation:} the signature aggregation operator is associative.
    \item \textbf{Efficient cancellation:} if $S$ is the predefined set of users that we need their aggregate
    signature, verifying an aggregate signature of $S-U$ can be done in time $O(T+|U|)$, if the aggregate
    signature of $S$ can be verified in $O(T)$.
\end{itemize}

>>>>

\begin{center}
    \begin{tabular}{||c||}
        \hline
        \textbf{Block} \\ [0.6ex]
        \hline\hline
        height: $h$                          \\ [1.2ex]
        commitment to the program database: $\mathbf{C}_{P}$             \\ [1.2ex]
        commitment to the heap database: $\mathbf{C}_{H}$               \\ [1.2ex]
        commitment to the ordered list of requests: $\mathbf{C}_{R}$        \\ [1.2ex]
        clustering directives: $dir$                        \\ [1.2ex]
        certificate of the validator assembly for \\
        the block with height $h - k$: $v \mhyphen cert_{h-k}$         \\ [1.2ex]
        certificate of the delegates for\\
        the previous block: $d \mhyphen cert_{h-1}$        \\ [1.2ex]
        previous block hash                           \\ [1.2ex]
        \hline
    \end{tabular}
\end{center}

@@

To validate a block three main conditions need to be validated: (i) commitments to the program and heap
database are resulted from applying the request list and clustering directives of the block to the previous AscEE
state, (ii) $v \mhyphen cert_{h-k}$ is valid, (iii) previous block is valid and has height $h - 1$.

@@

Verifying statement~\ref{eq:ci} can be done by either replaying the AscEE computation and performing the required
preprocessing and postprocessing steps, or alternatively by
verifying a computational integrity proof\footnote{More accurately we should call it an argument instead of a proof.
However, using the word argument can confuse a reader who is not familiar with the subject, so we avoid it here.}.
To use computational integrity proofs the verifier and prover need to
share an arithmetized representation of $\tau$ and use it for both proof generation and verification.

The Argennon Prover Machine provides a convenient and universal way for arithmetization of any Argennon
application. Moreover, since a compiled version of every Argennon application to the APM code is stored in the AscEE
program area, validators do not need to locally store the APM code of applications.

The Argennon protocol does not enforce the usage of the APM. Validators and PVC servers can use any argument system
with any arithmetization, and if required, the ASAR of an application can be used
for generating the appropriate arithmetization instead of the APM\@.

The certificate of validators, $v \mhyphen cert_{h-k}$, is an aggregate signature. Validating it requires accessing the
AscEE heap state at block $h-k-m$ to obtain public keys and stake values. Here $m$ is the total number of validator
assemblies and $k$ is the maximum allowed length of
the unvalidated chain. (See Section\ref{subsec:validators-committee})
Again, in addition to direct verification, a validator can use computational integrity proofs, received from the
Argennon cloud, to perform cheaper verification of this certificate.

For validating the previous block, instead of directly validating the content of the block, a validator only
verifies the block certificates. Verifying $d \mhyphen cert_{h-1}$ is straightforward. Verifying $v \mhyphen
cert_{h-1}$, which should be performed based on stakes at block $h-m-1$, can be cheaply done by using computational
proofs, obtained from the Argennon cloud.

@@

In summary, a validator validates a block by verifying three computational integrity proofs: $\pi_{\tau}$ which proves
the transition is correct, $\pi_{h-k}$ which proves the validity of the included certificate of block $h-k$ and
$\pi_{h-1}$ which proves the previous block has a correct certificate of validators. It should be noted that these
proofs are not a part of the block contents and therefore the exact argument system used for generating them is not
specified by the Argennon protocol.

@@

The Argennon network uses a parallel algorithm to produce block certificates and therefore the signature scheme needs
to satisfy certain properties:
\begin{itemize}
    \item \textbf{Associative aggregation:} the signature aggregation operator is associative.
    \item \textbf{Efficient cancellation:} if $S$ is the predefined set of users that we need their aggregate
    signature, verifying an aggregate signature of $S-U$ can be done in time $O(T+|U|)$, if the aggregate
    signature of $S$ can be verified in $O(T)$.
\end{itemize}

### 2022-09-26 tex/sections/consensus.tex
Fix readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Every block of the Argennon blockchain needs a certificate from both the committee of delegates and
the assembly of validators. A block is considered final after its \textbf{next} block receives \textbf{both} of
its certificates. In Argennon as long as more than half of the total stake of validators is controlled by honest users,
the probability of discarding a final block is near zero even if all the delegates are malicious.

>>>>

Every block of the Argennon blockchain needs a certificate from both the committee of delegates and
the assembly of validators. A block is considered final after its \textbf{next} block receives \textbf{both} of
its certificates. In Argennon as long as more than $2/3$ of the total stake of validators is controlled by honest users,
the probability of discarding a final block is near zero even if all the delegates are malicious.

### 2022-09-26 tex/sections/intro.tex
Fix readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

In case the main committee fails to generate new blocks or behaves maliciously, a special \emph{recovery protocol} is
initiated by validators.
This recovery protocol can recover the functionality
of the Argennon blockchain as long as more than $2/3$ of the total stake of the system is controlled by honest users
and any network partition resolves after a finite amount of time. The recovery protocol uses two main emergency
procedures to recover the functionality of the Argennon blockchain: \emph{Emergency Forking} and \emph{Emergency
Agreement} protocol.

In Argennon, a block is considered final after its \textbf{next} block gets certified by \textbf{both} the
delegates committee and its validator assembly.
The Argennon protocol ensures that as long as more than half of the total stake of validators is
controlled by honest users, the probability of discarding a final block is near zero even if all the delegates are
malicious.

@@

In addition to the ASAR, an Argennon application is stored on the blockchain in the Argennon Prover Machine (APM) code.
This code is used by validators for CI proof verifications. The Argennon Prover Machine is a virtual
machine tailored for efficient verification of AscEE computations by
argument systems. The APM has a minimal RISC architecture with a very compact instruction set. This ensures that
its transition function has an efficient circuit complexity.

>>>>

In case the main committee fails to generate new blocks or behaves maliciously, a special \emph{recovery protocol} is
initiated by validators.
This recovery protocol can recover the functionality
of the Argennon blockchain as long as more than $2/3$ of the total stake of every validator assembly is controlled by
honest users and any network partition resolves after a finite amount of time. The recovery protocol uses two main
emergency procedures to recover the functionality of the Argennon blockchain: \emph{Emergency Forking} and
\emph{Emergency Agreement} protocol.

In Argennon, a block is considered final after its \textbf{next} block gets certified by \textbf{both} the
delegates committee and its validator assembly.
The Argennon protocol ensures that as long as more than $2/3$ of the total stake of validators is
controlled by honest users, the probability of discarding a final block is near zero even if all the delegates are
malicious.

@@

In addition to the ASAR, an Argennon application is stored on the blockchain in the Argennon Prover Machine (APM) code.
This code is used by validators for CI proof verifications. The Argennon Prover Machine is a virtual
machine tailored for efficient verification of AscEE computations by
argument systems. The APM has a minimal RISC architecture with a very compact instruction set. This ensures that
its transition function has an efficient circuit complexity. However, the Argennon protocol does not enforce the usage
of the APM. Validators and PVC servers can use any argument system with any arithmetization, and if required, the ASAR
of an application can be used for generating the appropriate arithmetization instead of the APM\@.
